On Secure Delegation of SampBQP with a Classical Client

### 2019-11-23 preliminaries.tex
Restructure flow and add TODOs

We then define a model of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.

\begin{definition}
	A sampling problem $S=(D_x)$ is said to have a Quantum Prover Interactive Proof ($\QPIP$) with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

>>>>

We then define models of interation between a classical client and a quantum server. This is taken from \cite{mahadev_delegation}.

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a $\BPP$ machine.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_0$ with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ defined in the same way as in $\QPIP_{XZ}$ except that $\bbV$ is fully classical and cannot receive or measure qubits.
\end{definition}

### 2019-11-23 qpip.tex
Restructure flow and add TODOs

In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial. As seen in \cite{kitaev2002classical}, a prover, honest or not, cannot do better than sending $n$ identical copies of some state. As a result, a simple Chernoff bound would suffice. The same reasoning does not generalize to our case, so instead we give the following proof. We start by considering simpler inputs before moving on to the general case.

@@

\begin{algorithm}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\Require $\phi=\sum_i w_i\ket{\rho_i^{\otimes n+m}}\bra{\rho_i^{\otimes n+m}}$
		\Procedure{Amplification}{$\phi$}
		\State Apply $\mathcal{F}$ to first $n$ registers of $\phi$
		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
			\State Output the last $m$ registers
		\Else
			\State Reject
		\EndIf
		\EndProcedure
	\end{algorithmic}
\end{algorithm}

\begin{observation}
	\autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers
\end{observation}

@@

Now we consider the general case. We use \autoref{deFinetti}. Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily small. That is, with some arbitrarily small error in measurement results, we can assume without the loss of generality that the client receives an input of the simple form above. Hence concludes the proof.

\subsection{Getting the Output}

Thanks to having padded the circuit with identity matrices at the end, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation. So simply take $m$ to be high enough that it happens at least once with overwhelming probability. When it does, measure the entire register. All the errors up to this point are $O(\varepsilon)$, so will be the distance between this output distribution and the true one.

@@

\Ethan{Now use \cite{mahadev_delegation} to turn this into a server-client thing}

>>>>

Here we create a QPIP scheme for...  In the case for decision problems, it would be a simple Chernoff bound as in \cite{kitaev2002classical}. A prover, honest or not, couldn't do better than sending $n$ identical copies of some state. The same reasoning does not generalize to our case, so instead we give the following construction.

We first give an alternative characterization of $\QPIP_0$.

\begin{definition}
	A sampling problem $S=(D_x)$ is said to be in $\QPIP_{XZ}$, or has a $\QPIP_{XZ}$ protocol,  with completeness $c$ and soundness $s$ if there exists a pair of algorithms $(\bbP, \bbV)$ with the following properties with input $x$:
	\begin{itemize}
		\item $\bbP$ is a $\BQP$ machine.
		\item $\bbV$ is a hybrid quantum-classical machine. Its classical part is a $BPP$ machine. Its quantum part is a single-qubit register, on which the verifier can apply only $X$ or $Z$ measurements.
		\item There is a quantum channel between $\bbP$ and $\bbV$ that can transmit one qubit at a time.
		\item There is a classical communication channel between $\bbP$ and $\bbV$.
		\item (Completeness) After interacting with $\bbP$, $\bbV$ accepts with probability $\geq c$.
		\item (Soundness) Given $\bbP'$, if $(\bbP', \bbV)$ accepts with probability greater than $\delta$, then conditioned on this acceptance, $\bbV$'s outputs has distribution $\tilde{D}$ with $\norm{\tilde{D}-D_x}\leq s$.
	\end{itemize}
\end{definition}

\begin{theorem}
	$\QPIP_{XZ}=\QPIP_0$
\end{theorem}
\begin{proof}
	See \cite{mahadev_delegation}.
\end{proof}

\begin{theorem}
	$\SampBQP$ is in $\QPIP_{XZ}$.
\end{theorem}

@@

TODO Do something about this
\begin{algorithm}
	\floatname{algorithm}{Protocol}
	\caption{Amplification with simple input}
	\label{AlgAmp1}
	\begin{algorithmic}[1]
		\State The prover sends $\poly(n)$ copies of...
		\State The verifier picks $m+n$ copies...
		\State The verifier runs Chernoff bound on...
		\If{number of accepted copies $\geq (\frac{1}{2}-\frac{\varepsilon}{2})n$}
			\State Measure time step...
			\State Output the...
		\Else
			\State Reject
		\EndIf
	\end{algorithmic}
\end{algorithm}
TODO what's $n$?

TODO Talk about de Finetti's here.

Now we consider the general case. We use \autoref{deFinetti}. Let $n=l$ and $k=\poly(n)$, so $\sqrt{\frac{2l^2\ln\abs{A}}{k-l}}$ can be arbitrarily inverse-poly small. That is, with some small error in measurement results, we can assume without the loss of generality that the rest of the algorithm acts on an input of the form... TODO.

@@

So we pad the circuit with identity matrices at the end before constructing... TODO, if we measured $t>\frac{T}{2}$ on the time register, we would know that the other registers include the output of the required quantum computation. So simply take $m$ to be high enough that it happens at least once with overwhelming probability. When it does, measure the entire register. All the errors up to this point are $O(\varepsilon)$, so will be the distance between this output distribution and the true one.

@@
